---
title: "RoL Election TWFE Analysis"
author: "Brendon Krall"
date: '2022-08-16'
output: html_document
---

# Enviroment Setup
```{r, Housekeeping, message=FALSE, warning=FALSE}
rm(list=ls()) # Clear working memory 
library(readxl) # Load Excel files
library(magrittr) # Make all colnames lower case with no spaces
library(stringr) # String formatting and replacement
library(dplyr) # Data wrangling and manipulation
library(ggplot2) # Data visualization
library(tidyr) # Nesting and unnesting dataframes
library(purrr) # Map all function
library(broom) # Multiple linear regressions
library(lmtest) # Run linear regressions with robust standard errors 
library(multiwayvcov) # Generate robust standard 
library(sandwich) # Generate robust standard errors
library(stargazer) # Good way to report regression reports
```
# DiD Packages
```{r, message=FALSE, warning=FALSE}
library(bacondecomp) # Andrew Goodman-Bacon (2021). Difference-in-differences with variation in treatment timing.
library(did) # Brantly Callaway, Pedro H.C. Sant’Anna  (2020) Difference-in-Differences with multiple time periods.
library(DIDmultiplegt) # Clément de Chaisemartin, Xavier D’Haultfoeuille (2020). Two-Way Fixed Effects Estimators with Heterogeneous Treatment Effects.

# Package Source: https://asjadnaqvi.github.io/DiD/docs/02_R/
```

# Data Import
```{r, message=FALSE, warning=FALSE}
setwd("C:/Users/brend/OneDrive/Documents/GitHub/WB-RoL-Social-Movements")
df <- read_excel("Elections_Final_10.08.xlsx", sheet = 1)
```

# Prepare Linear Regression Model Terms and Dummy Variables
```{r}
# Create Year Fixed-Effect Variable 
df$year_dummy <- factor(df$Year)

# Create Constituency Fixed-Effect Variable 
df$constituency_dummy <- factor(df$`PA ID`)

# Create Treated 2008 and 2013 variable
df <- df %>% mutate(
#  treated_2008 = ifelse((Year <= 2008 & `Treated before 2008 elections` == 1), 1, 0),
#  treated_2013 = ifelse((Year >= 2013 & Treated == 1), 1, 0),
  treated = ifelse((`1st_visit_year`>= Year), 1, 0)
)

# Create Visits 2008 and 2013 variable Counts
#df <- df %>% mutate(
#  treated_2008_n = ifelse((Year == 2008 & Treated == 1), 'Visits before 2008 elections', 0),
#  treated_2013_n = ifelse((Year == 2013 & Treated == 1), 'N_visits', 0)
#)

# Remove observations with NA values for our outcome variable 
df <- df %>% filter(!is.na(Vote_Share))
```

# Subset Dataset for Regression Analysis
```{r}
# Restrict analysis to years between 2002 and 2008
df_02_08 <- df %>%
  filter(Year >= 2002 & Year <= 2008)

# Subset data by party affiliation 
df_pml <- df_02_08 %>%
  filter(`Party Initials` == 'PML')

df_pml_n <- df_02_08 %>%
  filter(`Party Initials` == 'PML-N')

df_pppp <- df_02_08 %>%
  filter(`Party Initials` == 'PPPP')
```


# DIDmultiplegt: Estimation in DID with Multiple Groups and Periods
```{r}
library(wooldridge)
Y = 'Vote_Share.1'
G = 'PA ID'
T = 'Year'
D = 'treated'
controls = c('count')

# PML
reg_pml1 <- did_multiplegt(df_pml, Y, G, T, D, controls, cluster=`PA ID`)

# PML-N
reg_pmln1 <- did_multiplegt(df_pml_n, Y, G, T, D, controls, cluster=`PA ID`)

# PPPP
reg_pppp1 <- did_multiplegt(df_pppp, Y, G, T, D, controls, cluster=`PA ID`)

## Source: https://cran.r-project.org/web/packages/DIDmultiplegt/index.html
```

# Goodman-Bacon decomposition for differences-in-differences with variation in treatment timing
```{r}
# PML
df_bacon_pml <- bacon(Vote_Share.1 ~ treated,
                  data = df_pml,
                  id_var = "PA ID",
                  time_var = "Year")
## Source: https://github.com/evanjflack/bacondecomp
```
# Brantly Callaway, Pedro H.C. Sant’Anna  (2020) Difference-in-Differences with multiple time periods
```{r}
## PML
# Estimate group-time average treatment effects using the att_gt function
pml <- att_gt(yname = "Vote_Share.1",
              gname = "1st_visit_year",
              idname = "PA ID",
              tname = "Year",
              xformla = ~1,
              data = df_pml,
              est_method = "reg"
              )
# Show the estimates of the group-time average treatment effects and their standard errors 
summary(pml)

# Plot the group-time average treatment effects
ggdid(pml)

# Make an event study plot in the did package
es <- aggte(pml, type = "dynamic")

# Plot the PML event study
ggdid(es)

## PML-N
# Estimate group-time average treatment effects using the att_gt function
pml_n <- att_gt(yname = "Vote_Share.1",
              gname = "1st_visit_year",
              idname = "PA ID",
              tname = "Year",
              xformla = ~1,
              data = df_pml_n,
              est_method = "reg"
              )
# Show the estimates of the group-time average treatment effects and their standard errors 
summary(pml_n)

# Plot the group-time average treatment effects
ggdid(pml_n)

# Make an event study plot in the did package
es_pmln <- aggte(pml_n, type = "dynamic")

# Plot the PML event study
ggdid(es_pmln)


## PPPP
# Estimate group-time average treatment effects using the att_gt function
pppp <- att_gt(yname = "Vote_Share.1",
              gname = "1st_visit_year",
              idname = "PA ID",
              tname = "Year",
              xformla = ~1,
              data = df_pppp,
              est_method = "reg"
              )
# Show the estimates of the group-time average treatment effects and their standard errors 
summary(pppp)

# Plot the group-time average treatment effects
ggdid(pppp)

# Make an event study plot in the did package
es_pppp <- aggte(pppp, type = "dynamic")

# Plot the PML event study
ggdid(es_pppp)

## Source: https://bcallaway11.github.io/did/
```

